Case Study (McKenna)

### 2020-09-29 Cases/mrp/Case Study (McKenna) .Rmd
Updating poststratification.

```{r}
# Importing the data. 
sample <- read_csv(here::here("Data", "sample.csv"))
proststrat <- read_csv(here::here( "Data", "poststrat.csv"))
true_popn <- read_csv(here::here( "Data", "true_popn.csv"))

# Add groups to data. 
proststrat_group <- proststrat %>% 
  mutate(group = row_number())

sample_group <- left_join(sample,
                          proststrat_group,
                          by = c(
                            "male" = "male", 
                            "age" = "age", 
                            "eth" = "eth", 
                            "income" = "income",
                            "state" = "state") )
```

@@

We will use Bayesian hierarchical modeling to take advantage of partial pooling to account for underweighted cells.

@@

```{r, eval = FALSE}
fit <- stan(
  file = here::here("Code", "mrp", "logit_hier.stan"),
  data = data_list,
  seed = 42 
)
```
```{r, eval = FALSE}
posterior_prob <- posterior_linpred(fit, transform = TRUE, newdata = poststrat)

?posterior_linpred

>>>>

```{r}
# Importing the data. 
sample <- read_csv(here::here("Data", "sample.csv"))
poststrat <- read_csv(here::here( "Data", "poststrat.csv"))
true_popn <- read_csv(here::here( "Data", "true_popn.csv"))

# Add groups to data. 
poststrat_group <- poststrat %>% 
  mutate(group = row_number())

sample_group <- left_join(sample,
                          poststrat_group,
                          by = c(
                            "male" = "male", 
                            "age" = "age", 
                            "eth" = "eth", 
                            "income" = "income",
                            "state" = "state") )
```

@@

We will use Bayesian hierarchical modeling to take advantage of partial pooling to account for underweight cells.

@@

```{r, eval = FALSE}
fit <- stan(
  file = here::here("Code", "mrp", "logit_hier.stan"),
  data = data_list,
  seed = 42 
)
```
```{r, eval = FALSE}
# I think we will need to use a for loop like they do in the downes model to construct our predictions into a format that we can then postratify them. I got this for loop from the downes code and I have just begun to adjust it for our model. 
 n_sim <- (n_iter * n_chain)/2   # They set the chains in their code but I don't think we did for our model so we'll have to take a look and see how to convert this 
n_pscell <- length(poststrat$N) # (n_pscell is the number of poststratification cells defined by the model)
n_state <- max(poststrat$STATE)
stanfit_final_ypred <- array(NA, c(n_sim, n_pscell))

for(l in 1:n_pscell){
    stanfit_final_ypred[,l] <- bernoulli_logit((x[n,] * beta[ll[n]])  # This is the part I am confused the most on. Just trying to specify the model in the right way to be able to make the service failure assumptions to then postratify. 
                                        )

stanfit_final_ps <- c(NA, n_sim)

# THEN WE CAN FINALY POSTSTRATIFY....I think 
for(s in 1:n_sim){
    stanfit_final_ps[s] <- sum(poststrat$N*stanfit_final_ypred[s,])/sum(poststrat$N)
  }

# This is just some other code that I am working on to try and look at a different way to post. I think this mainly comes from the original case study from Lauren. 
posterior_prob <- posterior_linpred(fit, transform = TRUE, newdata = poststrat)
